\thesistitle

### 2019-08-16 sections/discussion.tex

In this chapter, we discuss the results of our research and experiments.

\section{Clone Type Definitions}
In this study, we proposed a set of clone type definitions for which a refactoring opportunity is known. We based these clone type definitions on the clone type definitions that are commonly used in literature. The design of these clone type definitions entails some decisions that have a large impact on the clones we considered for refactoring in this study. In this section we discuss our clone type definitions as proposed in Section~\ref{sec:rtypes}.

@@

One method we think can be used to find more refactoring opportunities is to allow variability in expressions that have/return the same type. If expressions have/return the same type, they can be extracted to a parameter and the corresponding expression can be passed as a parameter. An example of this is displayed in Figure~\ref{fig:samereturn}. The only thing to watch out for is method that have side effects. Because methods may be executed in another point during execution, this might affect the functionality of the code.

@@

\section{Experimental setup}
In this section we discuss the setup of our experiments. We discuss alternative setups that could lead to other perspectives on the problem addressed.

>>>>

In this chapter, we discuss the results of our research and experiments.
% TODO: Sander - ik mis ergens in chapter nog interpretatie van je resultaten van H6, of heb ik iets gemist?

\section{Clone Type Definitions}
In this study, we proposed a set of clone type definitions for which a refactoring opportunity is known.
% TODO: Sander - is known is beetje gek
% TODO: Sander - zou ook uitleggen waarom we nieuwe definities nodig hadden
We based these clone type definitions on the clone type definitions that are commonly used in literature. The design of these clone type definitions entails some decisions that have a large impact on the clones we considered for refactoring in this study. In this section we discuss our clone type definitions as proposed in Section~\ref{sec:rtypes}.

@@

One method we think can be used to find more refactoring opportunities is to allow variability in expressions that have/return the same type. If expressions have/return the same type, they can be extracted to a parameter and the corresponding expression can be passed as a parameter. An example of this is displayed in Figure~\ref{fig:samereturn}. The only thing to watch out for is method that has side effects. Because methods may be executed in another point during execution, this might affect the functionality of the code.
% TODO: Sander - how would you try to solve this?

@@

\section{Experimental setup}% TODO: Sander - deze sectie is gek, soort combinatie van opzet en threats to validity, het kan wel maar loopt niet super lekker met het geheel
In this section we discuss the setup of our experiments. We discuss alternative setups that could lead to other perspectives on the problem addressed.
